Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations

### 2024-06-30 draft.tex
numerous updates

>>>>

\begin{remark}
    For reference, how the extension should work:
    suppose that $u \in H(\Omega)$ and let $f = du$.
    Suppose we have $u_1 \in H(T_1)$ with $du_1 = du$ over $T_1$. 
    We built $u'_2 \in H(T_2)$ such that 
    \begin{align*}
        \trace_F u_1 = \trace_F u'_2
    \end{align*}
    We let $u''_2 \in H(T_2)$ such that 
    \begin{align*}
        d u''_2 = f - d u'_2, \quad \trace_F u''_2 = 0
    \end{align*}
    Such $u''_2$ exists because 
    \begin{align*}
        \trace_F( f_2 - d u'_2 ) 
        &= 
        \trace_F f_1 - \trace_F d u'_2
        \\&= 
        \trace_F f_1 - \trace_F d u'_2
        \\&= 
        \trace_F d u_1 - \trace_F d u'_2
        \\&= 
        d \trace_F u_1 - d \trace_F u'_2
        \\&= 
        d \trace_F u_1 - d \trace_F u_1
        = 0
        .
    \end{align*}
    Setting $u_2 = u'_2 + u''_2$, we find 
    \begin{align*}
        d u_2 = d u'_2 + d u''_2 = d u'_2 + f - d u'_2 = f,
        \\
        \trace_F u_2 = \trace_F u'_2 = \trace_F u_1.
    \end{align*}
    That requires an extension from given partial boundary data. 
    Possible approaches:
    \begin{itemize}
        \item Reflect a neighborhood and multiply with cut-off function.
        \item Take traces from patch and extend onto new simplex. 
    \end{itemize}
\end{remark}
